---
title: "Random Forest Model"
author: ""
date: "`r format(lubridate::today(), '%d %b %Y')`"
output: html_document

params:
  dpath: !R data/boston.csv
  target_name: !R target
  outpath: !R assets
  name: "rf"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# find the root directory for the project and set that as wd
root_dir <- rprojroot::find_root(rprojroot::is_rstudio_project)
knitr::opts_knit$set(root.dir = root_dir)
```


## Overview

The notebook aims to:

1. Train a random forest model
2. Evaluate model performance
3. Save the model object as asset


## Load Libraries

```{r load, message=FALSE, warning=FALSE}
library(skimr)          # summary stats
library(tidyverse)      # data manipulation
library(tidymodels)     # modelling
library(highcharter)    # interactive visualization
library(janitor)        # clean column names, convert to snake case
```

## Import Data

```{r import, message=FALSE, warning=FALSE}
dat <- read_csv(params$dpath) %>%
  rename(target = params$target_name) %>%
  clean_names()
dim(dat)
```

 ## Preprocessing

- Convert variable class eg. make sure date is in correct format
- Variable validation
- Derive new features (make sure don't introduce leakage between train and test)


## Train and Test Split

```{r split}
set.seed(42)
sss <- initial_split(dat, prop = 3/4)
dat_train <- training(sss)
dat_test <- testing(sss)

dim(dat_train)
dim(dat_test)
```


## Recipe

Create a recipe of steps to be taken. Apply the recipe to train and test separately.

```{r train}
rec <- dat_train %>%
    recipe(target ~., data = .) %>%
    step_log(lstat) %>%
    step_nzv(all_predictors()) %>%       # zero variance filter             
    check_missing(all_predictors())      # check missing values

prepped <- prep(rec)

train <- prepped %>%
  juice()

test <- prepped %>%
  bake(new_data = dat_test)
```

## Random Forest

```{r fit}
fit <- rand_forest(mode = 'regression') %>%
  parsnip::set_engine(engine = 'randomForest') %>% # ranger
  fit(formula=formula(prepped), data = train)

fit$fit
```




## Evaluation

We calculate evaluation metrics on both train and test sets.

NB: If the model performs much better on train than on test, it is likely to be overfitting.

### Metrics

```{r model_metrics, message=FALSE, warning=FALSE}
# train
results_train = dat_train %>%
  bind_cols(predict(fit, new_data = train))
# test
results_test = dat_test %>%
  bind_cols(predict(fit, new_data = test))
# combine
scores = list(results_train, results_test) %>%
  map_dfc(~ yardstick::metrics(truth=target, estimate=.pred, data=.x)) %>%
  select(-contains('.estimator')) %>%
  select(-.metric1) %>%
  set_names('Metric', 'Train Score', 'Test Score')
kable(scores)
```



### Comparison of actuals VS predictions

```{r actual_vs_pred, message=FALSE, warning=FALSE}
GnT::plot_actual_vs_pred(data = results_test, xvar = "target", yvar = ".pred")
```




### Variable Importance

```{r variable_importance, echo=FALSE}
GnT::plot_var_importance(fit)

```

## Save Model Object

```{r save, message=FALSE, warning=FALSE}
GnT::save_mod(fit, scores, params$outpath, params$name)
```
